Missing The Point

### 2020-09-14 Manuscript.Rmd
Plot outcomes simulation

>>>>

## Some results

```{r echo=FALSE}
load("~/MissingThePoint/Data/results.Rdata")
results %>%
  ggplot() +
  geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=est, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=est, color = mech, linetype = as.factor(p))) +
  theme_classic()

# results %>% 
#   ggplot() + 
#   geom_hline(yintercept = 0.95) +
#   geom_point(aes(x=it, y=cov, color = mech, shape = as.factor(p))) + 
#   geom_line(aes(x=it, y=cov, color = mech, linetype = as.factor(p))) + 
#   theme_classic()

results %>%
  ggplot() +
  #geom_hline(yintercept = 0.3334) +
  geom_point(aes(x=it, y=CIW, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=CIW, color = mech, linetype = as.factor(p))) +
  theme_classic()

results %>%
  ggplot() +
  geom_hline(yintercept = 0.2090) +
  geom_point(aes(x=it, y=rsq, color = mech, shape = as.factor(p))) +
  geom_line(aes(x=it, y=rsq, color = mech, linetype = as.factor(p))) +
  theme_classic()

```
